---
title: "Case 2"
output:
  pdf_document: default
  html_notebook: default
  html_document:
    df_print: paged
---

# Summary

## Part 1 

- Through stepwise regression, only `Company size` is a significant feature with a p-value of 0.000919 and a beta of 1.4651.
- This stepwise model has a good fit, as it has an adjusted $R^2$ of 0.7299 and a p-value of 0.0001541.
- Thsis stepwise model generates the following function

$$
\text{Size of Purchase (\$1,000s)} = 128.7 + 1.4651 \times \text{Company Size (\$millions sales)} -41.07 \times \text{Similar Products}
$$

## Part 2

- There seems to be no linear relationship between the dependent variable (`Average sales`) and independent variable (`Hours worked per week` and `Number of Customers`)
- Plotting `Average sales` against `Hours worked per week` seems to be heteroscedatic, therefore ruling out the use of OLS
- However oddly, using OLS, we could get a (almost) good fit of p-value of 0.02468 and Adjusted R-squared of 0.968 with the following equation (with *S* as the `Average sales`, *C* as the `Number of Customers`, *H* as the `Hours worked per week`)

$$
\begin{split}
S = &4.788(10^3) \\
+ &2.356(10^1) C + 3.654(10^{-4}) C^2 - 6.346(10^{-6}) C^3 \\
- &3.850(10^2)H + 1.025(10^1) H^2 - 9.038(10^{-2}) H^3 + 5.997(10^{-19}) e^{H}
\end{split}
$$

## Part 3

- There is a quadratic relationship between `Sales ($ million)` and `Number of Employees`. 
- The quadratic model would follow the following model

$$
\text{Average Sales} = -93.21 + 1.4554 \times \text{No. of employees} + -0.0040 \times \text{No. of employees}^2
$$

- This quadratic model would be have an Adjusted R-squared of 0.7535 and p-value: 0.003084

\newpage

# Works

Importing various libraries
```{r message=FALSE, warning=FALSE}
library(tidyverse)
library(caret)
library(leaps)
library(MASS)
```

## Part 1

Import the data set and then generate `stepwise regression` model

```{r}
data_part1 <- read.csv('csv/part1.csv', header = TRUE)
# Fit the full model 
full.model_part1 <- lm(Size.of.Purchase...1.000s. ~ ., data=data_part1)
# Stepwise regression model
step.model_part1 <- stepAIC(full.model_part1, direction = "both", trace = FALSE)
summary(step.model_part1)
```

\newpage

## Part 2

Get the data and divide up the columns of data

```{r}
data_part2 <- read.csv('csv/part2.csv', header = TRUE)
# split the data into various columns
avg_sales <- data_part2$Average.Sales....million.
hours_work <- data_part2$Hours.Worked.per.Week
no_customer <- data_part2$Number.of.Customers
```

Plot the `Average Sales ($ million)` against `Hours Worked per Week`

```{r}
plot(hours_work, avg_sales,
     main = "Average sales and hours worked per week",
     ylab = "Average Sales",
     xlab = "Hours worked",
     pch=19)
```

We see that the data is **heteroscedatic**. Therefore, any method of regression using OLS directly on this set of data would be unfavoured. Then we plot the `Average Sales ($ million)` against `Number of Customers`

```{r}
plot(no_customer, avg_sales, 
     main = "Average sales and hours worked per week",
     ylab = "Average Sales",
     xlab = "Number of Customers",
     pch=19)
```

We see that the data has a possible outlier at (188, 13.8). There seems to be a weak relationship between the `Average Sales ($ million)` and `Number of Customers`. Then, we run a stepwise regression (however unwillingly, as it is unfavourable to run an OLS model with data that is heteroscedatic)

```{r}
full.model_part2 <- lm(avg_sales ~ poly(no_customer,3,raw=TRUE) 
                       + poly(hours_work,3,raw=TRUE) 
                       + exp(hours_work))
step.model_part2 <- stepAIC(full.model_part2, direction = "both", trace = FALSE)
summary(step.model_part2)
```

\newpage

## Part 3

Get the data and plot the scatter plot

```{r}
data_part3 <- read.csv('csv/part3.csv', header = TRUE)

plot(data_part3$Number.of.Employees,
     data_part3$Sales..............million., 
     main = "Sales against Number of employees",
     ylab = "Sales",
     xlab = "Number of employees", pch=19)
```

There seems to be a non-linear relationship between `Sales ($ million)` and `Number of Employees`. Therefore we try to do a non-linear regression for it. This looks like a quadratic relationship.

```{r}
sales <- data_part3$Sales..............million.
no_employees <- data_part3$Number.of.Employees


full.model_part3 <- lm(sales ~ poly(no_employees,2,raw=TRUE))
summary(full.model_part3)
```

We would also draw out the final graph for it.

```{r}
#generate range of 50 numbers starting from 30 and ending at 160
xx <- seq(110,220, length=50)
plot(no_employees, sales, pch=19,
     xlab="Number of Employees",
     ylab="Sales",
     ylim=c(20,40))
lines(xx, predict(full.model_part3, data.frame(no_employees=xx)), col="red")
```


